---
title: "P8105_hw6_rm3609"
author: "Runqi Ma"
date: "2018/11/26"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)
library(modelr)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

#Problem 1

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. 
Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO. Also omit Tulsa, AL. 
Modifiy victim_race to have categories white and non-white, with white as the reference category. 
Be sure that victim_age is numeric.
```{r}
homi_data = read_csv("./homicide-data.csv")

homi_data =
  homi_data %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         homi_solved = if_else(disposition == "Closed by arrest", 1, 0),
         victim_race = if_else(victim_race == "White", "White", "Non-White"),
         victim_race = fct_relevel(victim_race, "White"),
         victim_age = as.numeric(victim_age)) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```


For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
Save the output of glm as an R object; 
apply the  broom::tidy to this object; 
and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.
```{r}
bal_logre = 
  homi_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(homi_solved ~ victim_age + victim_sex + victim_race, data = . ,family = binomial())

bal_logre %>% 
  broom::tidy(conf.int = TRUE) %>% 
  mutate(OR = exp(estimate),
         conf_low_adj = exp(conf.low),
         conf_high_adj = exp(conf.high)) %>% 
  filter(term == "victim_raceNon-White")
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. 
Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
fuc = function(data) {
  broom::tidy(data, conf.int = TRUE)
}
  
each_city = 
  homi_data %>% 
  group_by(city_state) %>% 
  nest() %>%
  mutate(model = map(data, ~glm(homi_solved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
         model = map(model, fuc)) %>% 
  select(-data) %>%
  unnest() %>% 
  mutate(OR = exp(estimate),
         conf_low_adj = exp(conf.low),
         conf_high_adj = exp(conf.high)) %>% 
  select(city_state, term, OR, conf_low_adj, conf_high_adj) %>% 
  filter(term == "victim_raceNon-White")
 
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
each_city %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low_adj, ymax = conf_high_adj)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#Problem 2
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
bw_data = read_csv("./birthweight.csv")

bw_data = 
bw_data %>% 
  mutate(babysex = as.factor(babysex), 
         frace = as.factor(frace),  
         malform = as.factor(malform),  
         mrace = as.factor(mrace))
  
sum(is.na(bw_data))
```

Propose a regression model for birthweight. 
This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
bwt_model_step = lm(bwt ~ ., data = bw_data)
step(bwt_model_step, direction = 'both')

bwt_model = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + menarche + mheight + momage + mrace + parity + ppwt + smoken, data = bw_data)

bw_data %>% 
  add_predictions(bwt_model) %>% 
  add_residuals(bwt_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.25) + 
  geom_smooth()
```

Compare your model to two others:
One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
```{r}
cv_df =
  crossv_mc(bw_data, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble))

cv_df = 
  cv_df %>%
  mutate(
    model_1 = map(train, ~lm(bwt~blength + gaweeks, data = .x)),
    model_2 = map(train, ~lm(bwt~bhead + blength + babysex + babysex * bhead + babysex * blength + blength * bhead + babysex * blength * bhead, data = .x)),
    model_3 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + menarche + mheight + momage + mrace + parity + ppwt + smoken, data = .x))) %>% 
   mutate(
    rmse_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = str_replace(model, "3", "stepwise"),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


