---
title: "P8105_hw6_rm3609"
author: "Runqi Ma"
date: "2018/11/26"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)
library(modelr)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

#Problem 1

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. 
Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO. Also omit Tulsa, AL. 
Modifiy victim_race to have categories white and non-white, with white as the reference category. 
Be sure that victim_age is numeric.
```{r}
homi_data = read_csv("./homicide-data.csv")

homi_data =
  homi_data %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         homi_solved = if_else(disposition == "Closed by arrest", 1, 0),
         victim_race = if_else(victim_race == "White", "White", "Non-White"),
         victim_race = fct_relevel(victim_race, "White"),
         victim_age = as.numeric(victim_age)) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```


For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. 
Save the output of glm as an R object; 
apply the  broom::tidy to this object; 
and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.
```{r}
bal_logre = 
  homi_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(homi_solved ~ victim_age + victim_sex + victim_race, data = . ,family = binomial())

bal_logre %>% 
  broom::tidy(conf.int = TRUE) %>% 
  mutate(OR = exp(estimate),
         conf_low_adj = exp(conf.low),
         conf_high_adj = exp(conf.high)) %>% 
  filter(term == "victim_raceNon-White")
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. 
Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
fuc = function(data) {
  broom::tidy(data, conf.int = TRUE)
}
  
each_city = 
  homi_data %>% 
  group_by(city_state) %>% 
  nest() %>%
  mutate(model = map(data, ~glm(homi_solved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
         model = map(model, fuc)) %>% 
  select(-data) %>%
  unnest() %>% 
  mutate(OR = exp(estimate),
         conf_low_adj = exp(conf.low),
         conf_high_adj = exp(conf.high)) %>% 
  select(city_state, term, OR, conf_low_adj, conf_high_adj) %>% 
  filter(term == "victim_raceNon-White")
 
```

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}

```

